\newcommand{\datemod}{20 March 2018}

\documentclass[11pt, letterpaper]{article}
\usepackage[NoDate]{currvita} % no date because currvita only prints at bottom, and I want at top
\usepackage{enumitem}
\usepackage[margin=1.2in, tmargin=.90in, bmargin=.90in]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage[colorlinks, urlcolor=purple]{hyperref}
\usepackage{url}

\urlstyle{same} % for email to show up right
\tolerance=600 % how much bad word spacing in each line is tolerated

% load ArnoPro reg and bold variants as unified font
\setmainfont{ArnoPro}[
Extension = .otf,
UprightFont = *-Regular,
BoldFont = *-Bold]
\newfontface\conds{ArnoPro-Display.otf} % define \conds as new font
\renewcommand*{\cvlabelfont}{\conds} % set labels in condensed "display" font
\renewcommand*{\cvheadingfont}{\LARGE\bfseries} % LARGE heading
\newcommand{\compactspacing}{\setlength{\itemsep}{-0.35em}} % reduce space between resume items

\newcommand{\describe}[1] {
    \begin{itemize}[label=---, topsep=-0.5em, itemindent=0em, labelsep=0.5em, leftmargin=2em]
    \small
    \item#1
    \end{itemize}
}

\begin{document}
\thispagestyle{empty} % no page # on first page

\begin{cv}{\color{blue}{Eric A. Cioffi}} % pink is cool
\setlength{\cvlabelskip}{0.75em} % space under my name
\cvplace{} % empty place because currvita only prints at bottom, and I want at top
\noindent Los Angeles, \datemod

% set label column width to that of longest label
\settowidth{\cvlabelwidth} {\cvlabelfont Aug 2012 – May 2016} 
%\settowidth{\cvlabelwidth}{\cvlabelfont Independent Learning}
\begin{cvlist}{Contact}
    \item \href{mailto:ecioffi@usc.edu}{\nolinkurl{ecioffi@usc.edu}}
    $\mid$ 240-437-8592
\end{cvlist}

\begin{cvlist}{Education}
    \compactspacing
    
    \item[Aug 2017 – Present] University of Southern California, Viterbi School of Engineering:
    B.S. in Electrical Engineering, Minor in Physics, projected May 2020 --- 3.2 GPA
    \item[Sep 2016 – Jun 2017] University of California, Santa Cruz, Jack Baskin School of Engineering --- 3.8 GPA
    \item[Aug 2012 – May 2016] Albert Einstein High School, Kensington, Maryland
\end{cvlist}

\begin{cvlist}{Experience}
    \compactspacing

    \item[Oct 2017 – Present] Member, USC Formula SAE Racing Team, Chassis Division
    \describe{Using NX11 CAD, helped design movable pedal box to allow comfortable vehicle operation by drivers of different heights.}
    
    \item[Nov 2016 – Jun 2017] Volunteer, UC Santa Cruz Bike Coop
    \describe{Instructed and assisted clients; did everything from maintenance to extensive repairs.}
    
    \item[Jul – Aug 2014] Staff Assistant, TIC Summer Camp, Bethesda, Maryland
    \describe{Tutored children to facilitate their creation of games in Logo and Java.}
    
    \item[May – Jul 2014] Wilderness Program, Grand Staircase-Escalante National Monument, Utah
    \describe{Cultivated self-reliance absent modern technology, e.g., lit fires with self-made bow drill.}
\end{cvlist}

\settowidth{\cvlabelwidth}{\cvlabelfont 2012} %set label column width
\begin{cvlist}{Selected Projects \normalfont(\url{https://github.com/ecioffi})}
    \compactspacing
    
    \item[2017] VHF/UHF Antenna
    \describe{Designed and built frame to house antenna elements in position and to stand in attic. Used frequency-optimized antenna design that receives 8VSB modulated signals from 45 miles away.}
    
    \item[2017] Custom Bicycle Wheel
    \describe{Utilizing offset-drilled rim and modified hub, designed and built wheel to fit 11-speed cogset in 7-speed dropout spacing.}
    
    \item[2014] 2048 AI
    \describe{Using brute-force expectimax with minimalist evaluation function, AI wins fad phone game every play.}
    
    \item[2012] Square Root Algorithm
    \describe{Developed and tested algorithm that calculates square roots with only addition and bitwise operations.}
\end{cvlist}
\renewcommand*{\cvlistheadingfont}{\large\bfseries}

\begin{cvlist}{Honors}
    \compactspacing
    
    \item[2017] University of California, Santa Cruz Dean's List, Winter and Spring Quarters.
    \item[2016] Albert Einstein High School Mathematics Award, given to single Senior selected by department head.
    %of the ${\sim}$370 students
\end{cvlist}

\setlength{\cvlabelsep}{2em}
\settowidth{\cvlabelwidth}{\cvlabelfont Independent Learning} %set label column width
\begin{cvlist}{Skills}
    \compactspacing
    
    \item[Languages] C\textbackslash C++, java, python, Bash, \LaTeX, English, Japanese
    \item[Notable Coursework] Internet of Things; Computer Systems and Assembly Language; Linear Circuits
    
    \setlength{\itemsep}{-0.25em} % slightly more space than usual before the list because it starts higher than a regular line would for some reason
    \item[Independent Learning]
    \begin{itemize}[topsep=-0.5em, itemindent=0em, labelsep=0.5em, leftmargin=1em, itemsep=0em]
        \small
        \item Self-study of math and C++ enabled skipping AP Calculus AB in high school and testing out of EE155, Introduction to Computer Programming, at USC.
        \item Started in bicycle work by disassembling then reassembling old bike.
        \item Learned automotive repair from Internet and factory service manual for 1992 Maxima.
    \end{itemize}
    
    %\item[Miscellaneous:] Can drive manual transmissions
\end{cvlist}

\end{cv}
\end{document}
\endinput